Robust Energy-Aware Routing with Uncertain Traffic Demands

### 2015-01-17 paper.tex
write paper

In this paper, we propose a different approach that finds one energy-aware routing robust to a set of traffic 
matrices, in particular, to arbitrary traffic demands. Such a routing without energy consideration is known as 
the demand-oblivious routing, and is well studied. However, the problem becomes much more challenging when energy 
conservation is involved. To overcome the challenges, we first define a new metric, namely oblivious performance 
ratio with energy constraint, which reflects the MLUR distance from a routing to the optimal routing when 
certain energy conservation requirement is satisfied. We model the problem of minimizing the performance ratio, 
and analyze the lower and the upper bounds. Then, we propose Robust Energy-Aware Routing (REAR) to solve 
the problem in two phases. REAR select sleeping links based on extended robust link utilization or algebraic 
connectivity, and compute the routing based on a classical demand-oblivious routing algorithm. 
We evaluate our algorithms on real and synthetic topologies. The simulation results show that REAR can save 
XX\% of line card power while the performance ratio is less than XX.
\end{abstract}

@@

\includegraphics[width=4cm]{circle}
\includegraphics[width=4cm]{clique}

@@

\section{Experiments}
There is are experiments.

>>>>

In this paper, we propose a different approach that finds one energy-aware routing robust to a set of traffic 
matrices, in particular, to arbitrary traffic demands. Such a routing without energy consideration is known as 
the demand-oblivious routing, and is well studied. However, the problem becomes much more challenging when energy 
conservation is involved. To overcome the challenges, we first define a new metric, namely oblivious performance 
ratio with energy constraint, which reflects the MLUR distance from a routing to the optimal routing when 
certain energy conservation requirement is satisfied. We model the problem of minimizing the performance ratio, 
and analyze the lower and the upper bounds. Then, we propose Robust Energy-Aware Routing (REAR) to solve 
the problem in two phases. REAR select sleeping links based on extended robust link utilization or algebraic 
connectivity, and compute the routing based on a classical demand-oblivious routing algorithm. 
We evaluate our algorithms on real and synthetic topologies. The simulation results show that REAR can save 
19\% of line card power while the performance ratio is less than 34\%.
\end{abstract}

@@

\vspace*{0.2in}
\includegraphics[width=4cm]{circle}
\includegraphics[width=4cm]{clique}
\vspace*{0.2in}

@@

\section{Experiments and Results}
We implemented our algorithm on real world topology, including Abilene, Geant and Cernet2, and we use Gravity model to generate
random traffic matrix. Because we take an attribute $w$ to expand the traffic range from $1/w$ to $w$, when the $w$ increased the
traffic varied in wider range. Particularly, when the $w$ limit extremity, we say the traffic matrix is really random, and our 
algorithm is irrelevant with traffic.

\vspace*{0.2in}
\includegraphics[width=4cm]{opr_with_remove_links}
\includegraphics[width=4cm]{opr_with_power_saving}
\vspace*{0.2in}

In Figure, we take $w$ as 1.5 and observe that: when we switch off more links, the OPR is increased as well. 
It is obvious that when the topology
lose connectivity by removing links, the worst case of robust routing must be far away from the optimal case in origin topology. And
in Geant and Abilene, even in the origin topology, the OPR value still not be 1. It is reasonable, because our robust routing 
is used for a range of traffic, however the optimal routing is calculated for the specific traffic matrix. But fortunately, our robust
routing is only $24\%$ greater than the optimal routing even in its worst case of Geant. And we also see that the curve become 
cliffy in the end, because when we remove the links the toplogy lose too much connectivity and there alwasy one path between two vertices.
Obviously, the performance will become worse in the end. Lastly we say that although the OPR relation really different in different 
topology, but the curve still be similar with each other, they are exponetial curve correspond with their vertices amount.

On the other hand, we may concern how is the OPR varifying when the power saving achived besides the amount of removed links.
Of course the more we removed the links, the more power we saved, but how to quantify the power of one link is difficult. Green
TE proposed the simple power model for topology, which can be represented in Table x:

\vspace*{0.2in}
\includegraphics[width=8cm]{power_model}
\vspace*{0.2in}

We compute the power saving ratio as the total power of the removed links over the total power of all the links. And we can
save 19\% power with only 34\% worse than the worst case for all the traffic in Abilene topology. In Geant and Cernet2, 
the OPR is little higher. Also we can see that two ways for removing links perform almost the same at the begin in Geant,
and varified at the end. It shows that we may find another better way for removing the links in the future.

For computing the worst case, we generate 1000 traffic matrix for every topoloy and the $w$ with the Gravity Model.
We show the each result in the Figure x and x when we remove the first 4 links in each topology. In Abilene, the result 
is more tighter than Geant. Comparsion in two ways, we can see that in Abilene the AC method is worse than the ERLU one,
and the downmost zone is the same in two ways, because the robust routing is same in the origin topology.

\vspace*{0.2in}
\includegraphics[width=4cm]{exp2_nosort_abilene}
\includegraphics[width=4cm]{exp2_nosort_geant}
\vspace*{0.2in}

\vspace*{0.2in}
\includegraphics[width=4cm]{exp2_sort_abilene}
\includegraphics[width=4cm]{exp2_sort_geant}
\vspace*{0.2in}

From Figure xx and Figure xx, we sort the 1000 TMs by their OPR value, and see that most of the TMs are quite average. 
It is said that, our metric OPR is always not be achived for most traffic matrix.

We know when we compute the robust routing for specific topology, the $w$ is very important. When the $w$ limit extremely,
our robust routing is said without knowledge of traffic matrix. Figure xx, show the OPR varified when $w$ changes. The greater
the $w$ is, the greater the OPR is. It is obvious because when the $w$ is greater, the traffic matrix is random in more wider 
range, and our OPR is the worst case of all the traffic matrix.

\vspace*{0.2in}
\includegraphics[width=8cm,height=4cm]{exp3_w}
\vspace*{0.2in}
